Optimizing the Robotics Closet

### 2018-12-03 paper.tex
symbol fixes

shelf $s$ is represented as an ordered triple $(d, l, c)$, where $d$ is the
distance from the door in ``shelf-lengths'', $l$ is the length of the shelf, and

@@

Note about notation: $l^i_k$ indicates the length of item $k$ while $l^s_k$ indicates the

@@

$x$, $p_x$ and $s_x$ represent the item's probability and subsystem respectively. 

@@

>>>>

shelf $s$ is represented as an ordered triple $(d, L, c)$, where $d$ is the
distance from the door in ``shelf-lengths'', $L$ is the length of the shelf, and

@@

Note about notation: ($l^i_k$ indicates the length of item $k$ while $l^s_k$ indicates the

@@

$x$, $p_x$ and $s_x$ represent the item's probability and subsystem respectively. Let
there be $n_0$ shelves and $m$ items, $k$ subsystems, and $n_c$ be the number of 
connected components.)

@@

\\
